\chapter{Higher Dimensional Molecular Dynamics}

\section{MD Simulation packages}

Gromacs
Amber
CHARMM
NAMD
Openmm

\section{Forcefields}
Choice of forcefield


\section{Modifications}

Modifications that need to be made to the MD software to allow for higher dimensional simulations.

\subsection{Bonded forces}
The AMBER99 forcefield defines 4 bonded forces and also 2 non-bonded forces. The bonded forces consist of a harmonic bond force and harmonic angle force followed by two periodic torsional forces both proper and improper. The non-bonded forces are a Lennard-Jones force and a Coulomb force. 

The Bonded forces are used to approximate the chemical bonds of a molecule. The basic set of forces includes a harmonic bond, dihedral angle and torsional forces. Improper dihedral forces are also included to ensure that chirality is maintained in a molecule. 

The harmonic bond force provides a restoring force between two atoms to maintains a preferred distance.
\begin{equation}\label{md:1:harmonic_bond}
V_{HB} = \sum^{bonds}\frac{1}{2} K_b (r - r_0)^2
\end{equation}
\begin{equation}\label{md:2:harmonic_angle}
V_{\theta} = \sum^{angles}\frac{1}{2} K_{\theta} (\theta - \theta_0)^2
\end{equation}


 
\begin{enumerate}
\item Harmonic Bond
\item Harmonic Angle
\item Periodic Angle
\item Improper Dihedral Angle (Chirality)
\item LJ force
\item Coulomb force
\item PME approximations
\item Integration
\item Boundary Conditions
\item Ensembles
\item Thermostats
\item Barostats
\item Solvation
\item REMD / changes in dimensionality
\end{enumerate}


\newpage