\documentclass[12pt, a4paper, oneside]{report} 


\usepackage{amsmath} % AMS Math Package
\usepackage{amsthm} % Theorem Formatting
\usepackage{amssymb}	% Math symbols such as \mathbb
\usepackage{graphicx} % Allows for eps images
\usepackage{setspace}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[
margin=1.25 in,
includefoot,
footskip=30pt,
]{geometry}
\usepackage{chemfig}
\usepackage[sort&compress,numbers,super]{natbib}
\usepackage[version=3]{mhchem}
\usepackage[none]{hyphenat}
\usepackage{honours}

% This defines the "body" environment
\newenvironment{preamble}
{
	\clearpage
	\pagenumbering{roman}
	\setcounter{page}{1}
}

\newenvironment{body}
{
	\clearpage
	\pagenumbering{arabic}
	\setcounter{page}{1}
}


\spacing{1.5} 
\bibliographystyle{achemso}

% This defines the "abbreviations" environment
\newcommand{\abbrlabel}[1]{\makebox[3cm][l]{\textbf{#1}\ \dotfill}}
\newenvironment{abbreviations}{\begin{list}{}{\renewcommand{\makelabel}{\abbrlabel}}}{\end{list}}

\author{Paul D. Solomon}
\title{Protein Folding in Higher Dimensions}
\subtitle{Using higher dimensional space to improve speed of protein folding simulations}
\university{The University of Sydney}
\degree{Bachelor of Science (Advanced) (Honours) }
\school{School of Chemistry}
\submit{November 2017}


\begin{document}

\maketitle

% The "preamble" environment used roman numbering
\begin{preamble}
	
	\chapter*{Abstract}
	
	The first sentence of your abstract is critical, It is usually a brief 
	informational statement of your the results reported in your thesis. In 
	principle, the reader should have to go no further if the subject is of little 
	interest to him or her. Your abstract does not include a restatement of your 
	title. It should contain specific data. For example, a general statement that 
	an important measurement was made is insufficient; include the actual results 
	and their uncertainties.
	\\\\
	For a thesis you may like to write two or three paragraphs in your abstract. 
	That is, you may wish to use a paragraph for each of the major results in your 
	thesis.
	\\\\
	
	\newpage
	
	\chapter*{Acknowledgements and Statement of Contribution}
	You must acknowledge all assistance from staff and others on a separate 
	page of the thesis, immediately after the title page and before any general 
	acknowledgements, explaining their role briefly but precisely. You must give 
	details of contributors to the project. For example, were you part of a team 
	who performed the experiment, did someone write parts of the computer code, 
	take the observations, build some of the apparatus, or do some of the analytic 
	work? If any of your Honours research built on results previously obtained in 
	another research project (for example a TSP project) these results must be 
	clearly highlighted. Here you must also acknowledge any assistance that was 
	provided in thesis preparation. You must provide a signed and dated statement 
	of originality of the form: 
	\\\\
	\centerline{I certify that this report contains work carried out by myself}
	\centerline{except where otherwise acknowledge}
	\\\\\
	Signed:\\
	\rule[1em]{25em}{0.5pt} % This prints a line for the signature
	
	Date:\\
	\rule[1em]{25em}{0.5pt} % This prints a line to write the date
	\newpage
	
	\section*{Acknowledgements}
	This is the general statement thanking people. It is the appropriate place to 
	thank your supervisor, your family, your research group, your office mates, 
	the rest of the honours cohort, the pizza place down the road...
	\\\\
	
	\newpage
	
	% Here you make your table of contents
	\tableofcontents
	\newpage
	
	% Here you list your figures (or tables)
	\listoffigures
	\newpage
	% you may also like to list abbreviations used as a list of abbreviations or 
	%as a glossary
	\chapter*{Abbreviations}
	\begin{center}
		
		\begin{abbreviations}
			\item[ESR] Electron Spin Resonance
			\item[NMR] Nuclear Magnetic Resonance
		\end{abbreviations}
		
	\end{center}
\end{preamble}

% Now begin the body of your thesis 
% The "body" environment used arabic numbering
% Here each chapter is a separate document and latex incorporates them all 
% when it compiles the document
%
\begin{body}
	\input{chapter1.tex}
	\input{chapter2.tex}
	\input{chapter3.tex}
%	\input{Chapter4.tex}
%	
\end{body}

\begin{preamble}
	
	% Now for bibliography and appendices (if applicable). Again these are using 
	%roman numerals for the page numbers. 
	\begin{spacing}{1.0}
		
		\bibliography{honours}
		
	\end{spacing}
	%\input{Appendix.tex}
\end{preamble}
	
\end{document}